### 2020-08-21 sections/expertise.tex
Create expertise.tex

\cvsection{Languages \& Softwares}

@@

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}

\cvskill
{} 
{reading skills)} \\

\cvskill
{Programming} 
{R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}

\cvskill
{} 
{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}

\cvskill
{} 
{{\scshape xhtml}, Notepad{\footnotesize ++}} \\

>>>>

\cvsection{Expertise}

@@

\cvskill
{Interests}
{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}

\cvskill
{}
{systems, political participation, digital media, electronic government}\\

\cvskill
{Techniques} 
{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}

\cvskill
{} 
{network analysis, qualitative comparative analysis, topic modelling} \\
